Fabric-Elasticity Relationships of Tibial Trabecular Bone are Similar in Osteogenesis Imperfecta and Healthy Individuals

### 2021-07-28 09_Article/Simon_2021_Bone_Draft_V03.tex
Submission of the manuscript

\subsection{HR-pQCT}
HR-pQCT imaging (XtremeCTII, SCANCO Medical, Br\"{u}tisellen,
Switzerland) was performed at the distal tibia on all patients from both groups. Participants in the healthy group were scanned using an in-house protocol as described in \cite{Schenk2020}. Namely, the reference line was positioned at the proximal margin of the dense structure formed by the tibia plafond and three stacks were scanned proximal to this reference line, see Figure \ref{01_Healthy}. On the other hand, for participants in the OI group, the reference line is placed at the subchondral endplate of the ankle joint.  The mid-point of the scanned volume of interest was located at a distance of 7\% of total tibia length from the reference line \cite{GHASEMZADEH2017,Bonaretti2017}. Then, the scans were acquired according to the manufacturer's standard in vivo acquisition protocol, see Figure \ref{01_OI}. The scanned region according to the two different protocol are shown side by side in Figure \ref{01_ClinicalSections}. For both the healthy and the OI groups, each stack consisted of 168 slices and an isotropic voxel resolution of 61 \si{\micro}m. This led to a thickness of roughly 10.2 mm for each stack. Standardized scanning settings were used (voltage of 60 kVp, 900 $\mu$A, 100 ms integration time) for the healthy group as well as for the OI group. For the healthy group, motion artefacts of first, middle and last slice (i.e slices number 1, 252, and 504) were graded on a scale proposed by \citeauthor{Pialat2012} \cite{Pialat2012} of 1 (no motion artefacts) to 5 (extreme motion artefacts). The final grade of each scan was defined as the highest slice grade. For the OI group, as the scan consisted of one stack, only one grade was attributed using the same scale as for the control group. Scans were then processed independently of their quality grading. A summary of the scans grading is shown in Figure \ref{01_MotionArtefacts}.

@@

A similar study could be performed on radius XCTII reconstructions to generalise the above findings. Another limitation is the anatomical site scanned in control and OI group. The section scanned for the control group was at a fixed distance. On the other hand, the section scanned for the OI group was placed at a distance relative to the total length of the tibia. Nevertheless, this relative distance is aimed to be at the same location that the standard clinical section on average. Moreover, this study investigates mainly the fabric-elasticity relationships of trabecular bone and ROIs were matched to compare only architectural differences between healthy and OI trabecular bone. A final limitation is that the measurements were performed on different HR-pQCT devices which were not cross-calibrated. However, as they are the same model (XCTII) and the quality control measurement ensures $\pm$ 1\% precision on BMD, this is expected to have a minor impact. \\

>>>>

\subsection{HR-pQCT}
HR-pQCT imaging (XtremeCTII, SCANCO Medical, Br\"{u}tisellen,
Switzerland) was performed at the distal tibia on all patients from both groups. Participants in the healthy group were scanned using an in-house protocol as described in \cite{Schenk2020}. Namely, the reference line was positioned at the proximal margin of the dense structure formed by the tibia plafond and three stacks were scanned proximal to this reference line, see Figure \ref{01_Healthy}. On the other hand, for member of the OI group, the reference line is placed at the subchondral endplate of the ankle joint.  The mid-point of the scanned volume of interest was located at a distance of 7\% of total tibia length from the reference line \cite{GHASEMZADEH2017,Bonaretti2017}, see Figure \ref{01_OI}. Then, the scans were acquired according to the manufacturer's standard in vivo acquisition protocol. The scanned regions according to these two different protocols coincide approximately and are shown side by side in Figure \ref{01_ClinicalSections}. For both the healthy and the OI groups, each stack consisted of 168 slices and an isotropic voxel resolution of 61 \si{\micro}m. This led to a thickness of roughly 10.2 mm for each stack. Standardized scanning settings were used (voltage of 60 kVp, 900 $\mu$A, 100 ms integration time) for the healthy group as well as for the OI group. For the healthy group, motion artefacts of first, middle and last slice (i.e slices number 1, 252, and 504) were graded on a scale proposed by \citeauthor{Pialat2012} \cite{Pialat2012} of 1 (no motion artefacts) to 5 (extreme motion artefacts). The final grade of each scan was defined as the highest slice grade. For the OI group, as the scan consisted of one stack, only one grade was attributed using the same scale as for the control group. Scans were then processed independently of their quality grading. A summary of the scans grading is shown in Figure \ref{01_MotionArtefacts}.

@@

A similar study could be performed on radius XCTII reconstructions to generalise the above findings. Another minor limitation is the slightly different protocol for selection of the anatomical site scanned in the control and OI groups. The section scanned for the control group was at a fixed distance, while the section scanned for the OI group was placed at a distance relative to the total length of the tibia. Nevertheless, as shown in Figure \ref{01_ClinicalSections}, the locations compare well and the ROIs were matched for BV/TV and DA to compare the fabric-elasticity relationships. A final limitation is that the measurements were performed on different HR-pQCT devices which were not cross-calibrated. However, as they are the same model (XCTII) and the quality control measurement ensures $\pm$ 1\% precision on BMD, this is expected to have a minor impact. \\
